\documentclass[11pt]{scrartcl}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage[sexy]{evan}
\usepackage[normalem]{ulem}
\usepackage{hyperref}
\usepackage{mathtools}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdfpagemode=FullScreen,
    }
\usepackage[most]{tcolorbox}
\renewcommand{\dangle}{\measuredangle}

\renewcommand{\baselinestretch}{1.5}

\addtolength{\oddsidemargin}{-0.4in}
\addtolength{\evensidemargin}{-0.4in}
\addtolength{\textwidth}{0.8in}
% \addtolength{\topmargin}{-0.2in}
% \addtolength{\textheight}{1in} 


\setlength{\parindent}{0pt}

\usepackage{pgfplots}
\pgfplotsset{compat=1.15}
\usepackage{mathrsfs}
\usetikzlibrary{arrows}

\title{Bunch G3-4 AIMO}
\author{Azzam Labib (IG: haxuv.world)}
\date{G3-4 | \today}
\begin{document}
\maketitle

\section{G4 2019}
\begin{enumerate}
    \item Find the value of the following expression.
    \[2019 \div 7 + 2018 \div 9 + 2005 \div 7 + 2000 \div 9\]
    
    \item Given $10001 = 73 \times 137$, find the sum of the three greatest factors of $20192019$.
    
    \item There are 4 red marbles, 6 yellow marbles and 5 blue marbles in a bag. How many marbles should be picked up randomly to ensure 2 blue marbles are picked?
    
    \item Patrick paid \$133 for buying 4 cup noodles and 7 bottles of soft drink. Given that the cost of each cup noodle is 3 times of the cost of each bottle of soft drink. How many dollars is the price of each cup noodle?
    
    \item Given that both the base and the height of a triangle are integers in centimetres and the area of the triangle is 219 square centimetres. How many possible combination(s) of the base and the height is / are there?
    
    \item There is a number. If it is multiplied by 5, and then added with 4, then the result will be 74. What is this number?
    
    \item Given that both the length and the width of a rectangle are integers in centimetres. And the perimeter of the rectangle is 210 centimetres. How many square centimetres is the maximum area of the rectangle?
    
    \item Find the value of the following expression.
    $2019^2-1981^2$
    
    \item Find the value of the following expression.
    \[\frac{1}{2019} + \frac{2}{2019} + \frac{3}{2019} + \cdots + \frac{670}{2019} + \frac{671}{2019} + \frac{672}{2019}\]
    
    \item In Figure 10, a large rectangle is formed by 5 identical small rectangles. Given that the area of the large rectangle is 1470 square centimetres, how many centimetres is the perimeter of a small rectangle?
    
    \item If the nine-digit number $2019324AA$ is divisible by 7, find the value of A.
    
    \item There is a big lake with perimeter of 400 metres. Patrick, who lives beside the lake, wanted to plant trees around the lake. On the first day, starting from his home, he planted an apple tree every 4 metres. On the second day, starting from his home, he planted an orange tree every 10 metres if there is no apple trees at that position. How many trees has he planted in total?
    
    \item Oliver has some 1 dollar coins, 2 dollar coins and 5 dollar coins. Given that the number of 1 dollar coins is 14 times of that of 2 dollar coins, and the total value of the coins is 120 dollars. Find the number of 5 dollar coins.
    
    \item Find the value of the following expression.
    \[1000^2 - 998^2 + 996^2 - 994^2 + 992^2 - \cdots - 8^2 + 6^2 - 4^2 + 2^2\]
    
    \item Amy, Bella, Chris and Debby have 200 candies in total. Amy gave Bella 13 candies. Then Chris gave Debby 20 candies. Then Bella gave Chris half of all her candies. Finally Debby gave Amy 24 candies. Then they have the same number of candies. How many candies did Bella originally have?
    
    \item Four friends have some golden coins. Aiden and Beck have 32 coins together. Beck and Chris have 46 coins together. Chris and Dylan have 45 coins together. How many coins do Aiden and Dylan have together?
    
    \item Among the 2019 natural numbers from 1 to 2019, at least how many numbers need to be picked such that there must be two numbers having a difference of 103?
    
    \item A dormitory is allocating the rooms. If there are 6 students living in each room, there will be 12 students not having rooms; if there are 8 students living in each room, there will be exactly 5 vacant rooms. How many students are there?
    
    \item How many rectangles are there in Figure 19?
    
    \item There are 5 numbers, in which two of them are equal. After summing up 4 of these numbers in different ways, 4 sums are found: 163, 164, 165 and 166. Which one of these five numbers appeared twice?
\end{enumerate}

\section{G3 2019}
\begin{enumerate}
    \item Find the value of the following expression.
    \[15 + 20 + 25 + 30 + 35 + 40 + 45 + 50 + 55 + 60 + 65 + 70\]
    
    \item Find the value of the following expression.
    \[36 \times 7 + 18 \times 11 + 30 \times 5\]
    
    \item Given that A is 4 times more than B. Find the value of B if A is 100.
    
    \item Find the units digit of the result of the following expression.
    \[3 \times 6 \times 9 \times 2013 \times 2016 \times 2019\]
    
    \item A big square is formed of 16 identical small squares. If the perimeter of the big square is 256 centimetres, how many centimetres is the side length of a small square?
    
    \item Find the units digit of $\underbrace{2019 \times 2019 \times \ldots \times 2019}_{2019 \text{ '2019's}}$.
    
    \item A ribbon of 5 feet length is cut into 4 equal segments. How long is each segment in inches? (1 foot is equal to 12 inches)
    
    \item Flatbreads are pan-fried using a large pan. At most 5 flatbreads can be pan-fried on the pan at the same time. It takes 2 minutes (continuously) to finish frying each side of flatbreads. At least how many minutes does it take to pan-fry 12 flatbreads?
    
    \item Find the value of the following expression.
    \[2019 - 60 - 59 - 58 - 57 - 56 - 3 - 2 - 1\]
    
    \item Find the value of the following expression.
    \[111 \times  + 222 \times 333 + 333 \times 444 + 7679 \times 20\]
    
    \item Aiden, Beck and Chris have several game cards. The number of game cards Aiden has is 4 times as that Beck has. The number of game cards Beck has is 2 times as that Chris has. Now Aiden has 1400 game cards more than Chris. How many game cards does Beck have?
    
    \item There are 8 balloons with different colours. How many different combinations of colours are there if 2 of them are bought?
    
    \item In Figure 13, a large rectangle is formed of 7 smaller identical rectangles. Given that the perimeter of a small rectangle is 14 centimetres, how long is the perimeter of the large rectangle in centimetres?
    
    \item Dylan is 36 years younger than Aiden. The age of Aiden is 5 times as the age of Dylan. After how many years, the age of Aiden will be 3 times as the age of Dylan?
    
    \item Toy cars are sold in a toy store. In the morning, 20 more than half of toy cars are sold. In the afternoon, 12 less than half of the remaining toy cars are sold. 32 toy cars are remained at the end. How many toy cars does the toy store have originally?
    
    \item 4 warehouses are built along a road for every 10 kilometres, named A, B, C and D in the sequence. Now there are 30 tons of cargoes in warehouse A, 40 tons of cargoes in warehouse B, 30 tons of cargoes in warehouse C and 10 tons of cargoes in warehouse D. If the transportation fee is 5 dollars per kilometre per ton of cargoes, how many dollars is the minimum transportation fee if all cargoes are needed to be transported to one warehouse?
    
    \item Beck and Chris are doing the same division: Beck mistakenly decreases the dividend by 24 so the quotient decreases by 6. Chris mistakenly decreases the divisor by 2 so the quotient increases by 15. What is the correct quotient?
    
    \item Patrick copies 'AIMOISVERYVERYFUNNY' repeatedly. How many 'Y's are written down after Patrick has written down 1000 letters?
    
    \item On both sides of a road, 82 potted plants are placed along the road from one end to another. Every two adjacent potted plants are 25 metres apart. How long is the road in metres?
    
    \item Define $f(a)$ as $3a + 1$. Find the value of n if $f(f(n)) = 40$.
\end{enumerate}

\section{G3 2020}
\begin{enumerate}
    \item Find the value of the following expression.
    \[2020 - 1725 + 525 - 620 + 743 - 357\]
    
    \item Given that A is 2 times greater than B. Find the value of A if B is 2020.
    
    \item Aiden has 13 books more than Beck. They have 65 books in total. How many books does Aiden have?
    
    \item Four people, namely A, B, C and D, come to a well with 3, 1, 2 and 4 identical large buckets respectively. There is only one small bucket, which is used to draw water from the well. In what order should they draw water from the well, in order to make the total time they spent to be the least? (The time one spent includes his waiting time. If A spent 3 minutes and B spent 5 minutes, then the total time they spent is 8 minutes)
    
    \item Dylan has 4 types of fishing line, 6 types of fishhooks and 8 fishing rods. How many ways for him to choose one type of fishing line, one type of fishhooks and one fishing rod?
    
    \item A large square is formed of 9 squares with side length of 9 centimetres. What is the perimeter of the large square in centimetres?
    
    \item Aiden and Beck produce 483 parts together every day. The amount Aiden produced is 6 times of that of Beck. How many parts does Beck produce every day?
    
    \item It is known that a foot is equal to 12 inches. If a pipe is 5 feet and 5 inches long, then what is the total length of 7 pipes of the same kind? (Give the answer as 'A feet and B inches', where B must be smaller than 12. E.g. '12 feet and 3 inches')
    
    \item Find the value of the following expression.
    \[12^2 + 22^2 + 32^2 + 42^2 + 52^2 + 62^2 - 182^2 - 192^2 - 202^2\]
    
    \item Suppose today is Sunday, then when 2020 days are gone, what day of the week will that day be?
    
    \item There are 50 pupils in class 3A. 20 of them join sport team. 20 of them join choir. If 15 of them join none of the two teams, then how many of them join both teams?
    
    \item When a number is subtracted from other, the unit-digit of minuend 0 is mistakenly written as 6. The hundred-digit of subtrahend 1 is mistakenly written as 7. The difference obtained is 1321. What is the correct difference?
    
    \item From 202 to 2020 (including these two numbers), how many multiples of 9 are there?
    
    \item If five-digit number $2020A$ is divisible by 4, find the sum of possible value of A.
    
    \item Figure 15 is originally a square with side length of 10 centimetres. Small squares with side length of 1, 2, 3 and 4 centimetres are cut from its edges respectively (as shown in the figure). How many centimetres does the perimeter of the figure become?
    
    \item Cookies are sold in a bakery. In the morning, 3 more than half of the cookies are sold. In the afternoon, 4 more than half of the remaining cookies are sold. 29 cookies are remained at the end. How many cookies does the bakery have originally?
    
    \item How many rectangles are there in Figure 17?
    
    \item Find the value of the following expression.
    \[1111112 \div 9 - 111112 \div 90 + 11112 \div 900 - 1112 \div 9000 + 112 \div 90000 - 12 \div 900000 + 2 \div 9000000\]
    
    \item If $a + b = 2$ and $a^2 + b^2 = 2$, find the value of $8 - 12$.
    
    \item Chris starts driving at 10 am. He intends arriving the destination at 11:30 am. However, the car can only travel at 42 kilometres per hour. He arrives the destination at 12:15 pm finally. How fast does Chris intend to drive at, in kilometres per hour?
\end{enumerate}

\section{G4 2020}
\begin{enumerate}
    \item Find the value of the following expression.
    \[53 \div 7 + 53 \div 56 + 53 \div 37\]
    
    \item Find the value of the following expression.
    \[3636 \div 60 - 12 \div 9\]
    
    \item Find the least common multiple of 7, 11 and 13.
    
    \item If the price of 2 boxes of candies equals to 3 boxes of chocolates, and the price of 7 boxes of candies and 2 boxes of chocolate is 200 dollars, what is the price of a box of candies and a box of chocolates in dollar?
    
    \item Amy had some candies. She ate 4 candies more than a half of the total amount, after that, 22 candies are left. How many candies did she have originally?
    
    \item Find the value of the following expression.
    \[\sqrt{2020 \times 20}\]
    
    \item Find the thousands digit of $\left(\frac{2020}{2020}\right)^{2020}$.
    
    \item In Figure 8, what is the total area of the figure in square centimetres?
    
    \item The process "$\boxed{\quad}$" has the following results:
    \begin{align*}
        \boxed{1} &= 10 \\
        \boxed{4} &= 16 \\
        \boxed{5} &= 12 \\
        \boxed{24} &= 18
    \end{align*}
    Find the value of $\boxed{2 \quad 16 \quad 15 \quad 25}$.
    
    \item If the least common multiple of the natural number A and 2020 is 60600, find the smallest value of A.
    
    \item Beck and his friends buy a The Journey to the West together. If each person pays 7 dollars, 39 more dollars are needed. If each person pays 11 dollars, 9 dollars are remained. How many dollars is a The Journey to the West?
    
    \item Debbie's birthday is on the 29$^{th}$ February. If her birthday in 2020 is Saturday, then what day of the week is her next birthday?
    
    \item Figure 13 shows a figure formed by three identical rectangles and a regular hexagon, if the perimeter of each rectangle is 12 centimetres, what is the perimeter of the figure in centimetres?
    
    \item From 1 to 100 (including 1 and 100), at least how many numbers are drawn randomly to ensure that there are two numbers which have 2 or more common factors?
    
    \item Aiden and Beck have 122 candies in total in the beginning. Beck gives a half of his candies to Aiden. Then, they each eat 11 candies. After that, Aiden gives a half of his left candies to Beck. Eventually, Beck has 18 candies more than Aiden. How many candies does Aiden have in the beginning?
    
    \item Among the 2020 natural numbers, which is from 1 to 2020, how many numbers that contain exactly one '2' and one '3' in digits are there?
    
    \item Find the value of the following expression.
    \[20202019 \times 20182017 - 20202018 \times 20182016\]
    
    \item In Figure 18, how many rectangles are there which contains exactly two black dots?
    
    \item If a number is divisible by 17, find the largest possible value of the remainder when that number is divided by 102.
    
    \item Aiden, Beck and Chris celebrate their birthday together. The age of Aiden is 2 times of Beck. 4 years after, the age of Aiden will be 3 times of Chris. If the sum of the current ages of Aiden, Beck and Chris is 78, how old is Beck this year?
\end{enumerate}

\section{P4 India}
\begin{enumerate}
    \item Find the perimeter of the figure below (in cm).
    
    \item 313 boy scouts are divided into groups and each group has at most 7 scouts. At least how many groups can be divided this way?
    
    \item Find the value of $480 \div 4 + 480 \div 6 + 480 \div 10$.
    
    \item Find the 21$^{st}$ term of the arithmetic sequence 27, 35, 43, 51, \ldots
    
    \item The difference between A and B is 24. A is 9 times of B. Find the value of A.
    
    \item There are a total of 30 chickens and rabbits in a farm. The animals have a total of 86 legs. What is the difference between the number the chickens and the rabbits?
    
    \item There are 7 pairs of green socks, 6 pairs of white socks, 5 pairs of red socks and 2 pairs of blue socks in a wardrobe. One person is asked to close his eyes, and draw the socks 1 pair at a time. At least how many pairs of socks should be drawn so that among the drawn socks 4 pairs of those have the same colour?
    
    \item If a 5-digit number $81075A$ is divisible by 11, find the value of A.
    
    \item When a five-digit number $27995A$ is divided by 9, the remainder is 4. Find the value of A.
    
    \item Find the value of $\frac{12}{22} + \frac{13}{24} + \frac{17}{36}$.
    
    \item The amount of Amy's pocket money each day is 3 times as much as the pocket money of Flora's. And the amount of Pearl's pocket money is \$7 more than Amy's. If they have \$980 of pocket money each week, how much pocket money does Pearl have each day?
    
    \item Each of the numbers from 1 to 10 are filled in the circles in the figure so that the sum of each side of the pentagon is 14. What number should be filled in the circle with an A?
    
    \item 10 people takes 5 days to complete one-fourth of a task. How many days are needed for 8 people to finish the same task?
    
    \item Charles has \$40 in the bank at the beginning. Starting from 1$^{st}$ February, Charles' mother will give Charles pocket money equal to the amount of money in the bank, and Charles saves \$5 every day in the bank. Until the night of the 16$^{th}$ of February, how much (in \$) did Charles' mother gave Charles?
    
    \item Numbers are drawn from the 60 integers 1 to 60. At least how many numbers are drawn at random to ensure that there are two numbers whose difference is 10?
    
    \item A 200-digit number is in the form of '393939\ldots'. The product of digits of the number is calculated, find the unit digit of the product.
    
    \item The figure is formed by 2 squares. Find the area of the shaded region (Hint: Consider the relationship between the area of triangle and the area of rectangle)
    
    \item If $ABCD$ is a 4-digit number divisible by 8 and both $ABC$ and $DCB$ are divisible by 8. Find the smallest possible value of $ABCD$.
    
    \item There are some chicken and rabbits. The animals have 304 legs in total. If we count the number of legs using the number of chicken as the number of rabbit, and using the number of rabbit as the number of chicken, there are 338 legs instead. How many chickens are there?
    
    \item When a five-digit number is divided by 33, the remainder is 11. Find the largest possible value of the number.
\end{enumerate}

\section{G4 2020}
\begin{enumerate}
    \item In the figure, $ABCD$ is a rectangle. The lengths of AE, $EF, FG, GH, HI, IJ$ and $JC$ are 20, 22, 24, 26, 28, 30 and 32 centimetres respectively. What is the difference between the areas of octagon $AEFGHIJD$ and $BEFGHIJC$ in square centimetres?
\end{enumerate}

\section{G4 2017}
\begin{enumerate}
    \item Find the number of positive factors of 35.
    \item Find the sum of all positive factors of 35.
    \item If the sum of two positive integers is 22, how many combinations of these two numbers are there? ($1$ and $21$ are counted as 1 combination only)
    \item Among the 36 natural numbers from 1 to 36, at least how many numbers have to be picked so that there must be 2 numbers whose difference is 18?
    \item Find the remainder when $19 \times 20 \times 21$ is divided by 9.
    \item Find the value of the following expression: \\
        $11 + 34 - 66 + 11$
    \item Fill in "$+$" or "$-$" in the blanks to make the calculation below valid. (Please write down the symbols in order on the answer sheet) \\
        $1\_ 2 \_ 3\_ 4 \_ 5 \_ 6 = 13$
    \item Two brothers have 127 candies. The elder brother gives the younger brother half of his candies. The younger brother, after eating 16 candies, returns 24 candies to the elder brother. It ends up that the number of candies of the elder brother is twice of that of the younger brother. How many candies does the younger brother have in the beginning?
    \item 5 bags of rice, 6 bags of soybeans and 9 bags of red beans weigh 60 kilograms, while 17 bags of rice, 18 bags of soybean and 27 bags of red beans weigh 200 kilograms. So how many kilograms does 1 bag of rice weigh?
    \item The shaded part is a square. How many centimetres is the perimeter of the largest rectangle?
    \item Ronny runs after Sunny at a speed of 25 km/h. In the beginning, Sunny is 3 km ahead of Ronny. If Ronny manages to meet Sunny 12 minutes later, how many kilometres does Sunny run each hour?
    \item Find the value of the following expression: \\
        $317 - 311 + 305 - 35 + 29 - 23$
    \item The ages of Mickey and Chesney add up to 95. The age of Mickey is 25 more than 4 times that of Chesney. Find the age of Mickey.
    \item A 7-digit number $2017\,4AA$ is divisible by 12. Find the sum of possibilities of A.
    \item There are two positive integers. Their sum is 143 and their product is 1080. Find the greater number among these two numbers.
    \item Among the 2000 natural numbers from 1 to 2000, at least how many numbers have to be picked at random so that there must be two numbers whose sum is 2017?
    \item A spider has 8 legs but no wings; A dragonfly 6 legs and 2 pairs of wings; A Cicadas 6 legs and 1 pair of wings. Now there are 27 insects of these three kinds. They have 180 legs and 25 pairs of wings in total. How many cicadas are there?
    \item If a number is divisible by 26, find the largest possible value of the remainder when that number is divided by 91.
    \item For an arithmetic sequence of more than 10 terms, each term is added by the same number. It ends up that the sum of the arithmetic sequence is increased by 111. Find the sum of all possible values of the number of terms.
    \item Figure 20.1 shows some numbered squares. If squares are to be tiled up to 2017 following the pattern, find the number in the square which is just above 127.
\end{enumerate}

\section{G3 2017}
\begin{enumerate}
    \item 6 different three-digit numbers can be formed using the digits "3", "6" and "8". Find the sum of these 6 three-digit numbers.
    \item There are 352 passengers on the train in the beginning. Upon arrival at the station, 175 passengers get off and 169 passengers get on. How many passengers are there on the train now?
    \item The number $20170312201703122017\ldots$ is written on and on. What is the $90^{th}$ digit?
    \item Find the value of the following expression: \\
        $1111 \div 111111111$
    \item Yolanda is 4 years older than her younger brother. Her father is 5 years younger than her mother. Yolanda's mother is now 40 years old. The age of Yolanda's father is 5 times that of Yolanda. How many years old is Yolanda's younger brother?
    \item A restaurant spends 540 dollars to buy 20 cups and 20 plates. A cup costs 3 dollars more than a plate. How much is a plate?
    \item Find the units digit of \\
        $88 \text{ "3"'s}$
    \item If $a \circ b = a + b + ab$, find the value of $5 \circ 8 \circ 3$.
    \item Find the remainder when $2017\,2017\,2017\ldots2017$ (with 2017 "2017"'s) is divided by 9.
    \item Figure 10.1 is formed by several squares of different sizes, where the numbers stand for their areas. Find the perimeter of figure 10.1.
    \item In the calculation below, the divisor and the quotient are equal. What is the least value of the dividend? \\
        $\square \div 12 = 12$
    \item 42 trees are planted along a road from one end to another on both sides. Every two adjacent trees are 8 metres apart. How long is the road in metres?
    \item 2 lawn mowers can clear a lawn of 80 square metres in 5 hours. At such rate, how many hours does it take for 5 lawn mowers to clear a lawn of 400 square metres?
    \item Split the 4 numbers 6, 2, 0 and 9 into 2 groups and form 2 two-digit numbers respectively so that their product is maximized. Find the product.
    \item In a multiplication of two numbers, the units digit 4 in one of the numbers is mistakenly written as 9 and as a result the product acquired is 722. If the correct product is 532, find the larger number.
    \item If $a \diamond b = \begin{cases}
        2a + b & \text{if $a \geq b$} \\
        2b + a & \text{if $a < b$}
    \end{cases}$, find the value of $(116 \diamond 16) \diamond (2 \diamond 8)$.
    \item The four members in Mandy's family have their ages add up to 99. Her brother is 8 years younger than Mandy. Dad is 3 years older than Mum. 10 years ago, the family ages added up to 65. How old is Mum this year?
    \item The digit sum of each of several three-digit even numbers is 8, with no repeated digits. How many such three-digit even numbers are there?
    \item Maffia enters the password "394052186" when she comes to the door. The gatekeeper says she has swapped two of the numbers. How many passwords at most does Maffia need to enter more?
    \item There are 55 cards. "1" is written on 1 card, "2" on 2 cards, "3" on 3 cards, \ldots, "10" on 10 cards. Now several cards are picked so that the sum of the numbers on all cards is 312. How many cards can be picked at most?
\end{enumerate}
\end{document}