\documentclass[11pt]{scrartcl}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage[sexy]{evan}
\usepackage[normalem]{ulem}
\usepackage{hyperref}
\usepackage{mathtools}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdfpagemode=FullScreen,
    }
\usepackage[most]{tcolorbox}
\renewcommand{\dangle}{\measuredangle}

\renewcommand{\baselinestretch}{1.5}

\addtolength{\oddsidemargin}{-0.4in}
\addtolength{\evensidemargin}{-0.4in}
\addtolength{\textwidth}{0.8in}
% \addtolength{\topmargin}{-0.2in}
% \addtolength{\textheight}{1in} 


\setlength{\parindent}{0pt}

\usepackage{pgfplots}
\pgfplotsset{compat=1.15}
\usepackage{mathrsfs}
\usetikzlibrary{arrows}

\title{Additional Material 1 Komodo Math 2024}
\author{Azzam Labib (IG: haxuv.world)}
\begin{document}
\maketitle

\begin{enumerate}
\item Andy has 4 fewer stamps than his sister Betty, and Betty has 6 more than their little brother Charlie. If together they have 74 stamps, how many stamps does Charlie have?

\item In a survey of 120 students, 54 said they liked playing football, 65 said they liked playing badminton, and 27 students said they liked both playing football and badminton. How many students disliked both playing football and badminton?

\item Find the ones digit in $(37^{52})$.

\item Light bulbs are on sale, so Ariana buys 7 packages. Each package has 4 bulbs in it. The letter $b$ stands for the total number of bulbs. Which equation can you use to find $b$?

\item Jenny is helping her mom blow up balloons for their party. Jenny blew up 7 red balloons. She also blew up 8 more blue balloons than red balloons and 5 more green balloons than red balloons. How many balloons did Jenny blow in total?

\item Which of the calculations below has a result with a remainder of 3? (No calculation provided)

\item A triangle has 3 sides: 6cm, 8 cm, and 10cm. What type of triangle is it?

\item A bag contains 10 marbles: 4 red, 3 blue, and 3 green. If a marble is randomly chosen from the bag, what is the probability that it is not red?

\item There are 5 different colors of jelly beans in a jar: red, blue, green, yellow, and purple. How many different ways can you choose 3 jelly beans from the jar if the order in which you choose them doesn't matter?

\item If the digits of the number 234 are rearranged to form the largest possible three-digit number, what is the difference between the largest and smallest possible numbers that can be formed?

\item In a math quiz, Ali scored 15 points less than Ben, who scored 95 points. Chloe scored half as many points as Ali. What is their mean score?

\item An athlete practiced for a 100-meter sprint race. He ran the track 40 times. The following table shows the time (in seconds) required for each athlete to complete one run. What is the median of her running times (in seconds)?

\item A die is rolled twice. What is the probability that the two numbers are equal?

\item The perimeter of a square is 48 cm. What is the area of the square?

\item Tommy has \$5 in his piggy bank. He wants to buy a game that costs \$28. He plans to save some money each week to buy the game. He thinks that if he saves $x$ dollars each week, he will have enough money to buy the game in 8 weeks. Find $x$.

\item Tom has $m$ toy soldiers, which he divides into 8 groups of 6 soldiers each. And John has $n$ toy soldiers, which he divides into 12 groups of 4 soldiers each. If $m$ and $n$ stand for the number of Tom's and John's toy soldiers, which comparison is correct according to the statement above?

\item It is given that $(x+12)(x-4) = x^2 + 8$. What is the value of $x$?

\item How many times 2 appears in the counting numbers 1 to 500?

\item If I place all three operational symbols $+$, $-$, and $\times$ in all possible ways into the blanks of the expressions $8 \_ 7 \_ 9 \_ 6$, one symbol per blank, each resulting expression will have a value. What is the largest of these values?

\item In a candy store, there are 4 different types of candy bars, 3 different types of gummy candies, and 2 different types of lollipops. How many different ways can you choose one item from each of the three categories?

\item In the figure below, the area of field C is 25 units squared. The difference between area A and area B is $\_\_\_\_$ units squared. (Write only in numbers.)

\item The sum of the father's and the son's ages is 70 years. The father's age was 3 times the son's age 5 years ago. How old is the son now? (Write your answer only in numbers.)

\item The following chart shows the number of houses that are currently being repaired in blocks A, B, C, D, and E. The average of the number of houses that is being repaired in each block is $\_\_\_\_$. (Write your answer only in numbers.)

\item In the trapezoid below, $AB:CD$ is $3:2$, and the area of the triangle $ACD$ is 12 units squared. The area of triangle $ABC$ is $\_\_\_\_$ units squared. (Write your answer only in numbers.)

\item A number has 3 digits. The digit in the hundreds place is three times the digit in the tens place, and the digit in the tens place is twice the digit in the ones place. The sum of all the digits in the number is 9. What is the number? (Write only in numbers.)

\item Andre asks his teacher her age. She replied, "My age now is a prime number, but after my next birthday it will be a number divisible by 9." Assuming her age is below 70 and above 20, how old is she now? (Write your answer only in numbers.)

\item Consider the following equation: $(x^2 + 8x + 15) / (x+3) = x + 5$. It's known that if $x = 1$, then $y = 6$. If $x = 3$, then $y = \_\_\_\_$. (Write your answer only in numbers.)

\item A teacher gave ten tests during the year, each carrying the same weight. If Mike had gotten 20 more points on the last test, his average would have become 91. What was his actual average? (Write only in numbers.)

\item A game booth has 3-point, 5-point, and 10-point targets. Clara hit 15 targets and scored 84 points altogether. Also, the number of hit on each point is different. How many 3-point targets did she hit?(Write your answer only in numbers.)

\item Four students, Ali, Ben, Clara, and Dony, attended a meeting. In this meeting: Ali shook hands with three students. Ben shook hands with two students. Clara shook hands with one student. How many students did Dony shake hands with? (Write your answer only in numbers.)
\end{enumerate}
\end{document}