\documentclass[11pt]{scrartcl}
\usepackage{graphicx}
\graphicspath{{./}}
\usepackage[sexy]{evan}
\usepackage[normalem]{ulem}
\usepackage{hyperref}
\usepackage{mathtools}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdfpagemode=FullScreen,
    }
\usepackage[most]{tcolorbox}
\renewcommand{\dangle}{\measuredangle}

\renewcommand{\baselinestretch}{1.5}

\addtolength{\oddsidemargin}{-0.4in}
\addtolength{\evensidemargin}{-0.4in}
\addtolength{\textwidth}{0.8in}
% \addtolength{\topmargin}{-0.2in}
% \addtolength{\textheight}{1in} 


\setlength{\parindent}{0pt}

\usepackage{pgfplots}
\pgfplotsset{compat=1.15}
\usepackage{mathrsfs}
\usetikzlibrary{arrows}

\title{Divisibility}
\author{Compiled by Azzam}
\begin{document}
\maketitle
\section{Ez Pz}
\begin{enumerate}
    \item Find the remainder when $13^{16} - 2^{16}$ is divided by 165.
    % From image_8d46c4.png (Practice Question 3)

    \item Show that $13 | 2^{70} + 3^{70}$.
    % From image_8d46c4.png (Practice Question 4)

    \item Show that $2^n \nmid n!$ for any integer $n \ge 1$.
    % From image_8d46c4.png (Practice Question 5)

    \item Find all positive integers $n$ such that $n!$ ends with exactly 1000 zeros.
    % From image_8d46e3.png (Practice Question 6)

    \item Find all positive integers $n$ such that $n^2+1$ is divisible by $n+1$.
    % From image_8d46e3.png (Practice Question 7)

    \item Show that $n^4 - 20n^2 + 4$ is not a prime number for any integer $n$.
    % From image_8d46e3.png (Practice Question 8)

    \item If $p$ is a prime number such that $p > 3$, show that $p^2-1$ is divisible by 24.
    % From image_8d46e3.png (Practice Question 9)

    \item Let $a, b, c$ be positive integers such that $a^2+b^2=c^2$. Show that $ab$ is divisible by 12.
    % From image_8d46e3.png (Practice Question 10)
\end{enumerate}

\section{Challenge}
\begin{enumerate}[resume]
    \item Find all positive integers $n, a,$ and $b$ such that $n^{b}-1 | n^a+1$.
    
    \item (1999 IMO) Find all pairs of positive integers $(x,p)$ such that $p$ is prime, $x \le 2p$, and $x^{p-1}$ divides $(p-1)^x+1$.
    
    \item (1999 AIME) Find the greatest positive integer $n$ such that $(n-2)^2(n+1)/(2n-1)$ is an integer.
    
    \item (1998 IMO) Determine all pairs $(a,b)$ of positive integers such that $ab^2+b+7$ divides $a^2b+a+b$.
    
    \item (2003 IMO) Determine all pairs of positive integers $(a,b)$ such that $a^2 / (2ab^2-b^3+1)$ is a positive integer.
    
    \item (1972 Putnam) Show that if $n$ is an integer greater than $1$, then $2^n-1$ is not divisible by $n$.
    
    \item (1990 IMO) Determine all integer $n>1$ such that $(2^n+1)/n^2$ is an integer.
    
    \item (1988 IMO) Let $a$ and $b$ positive integers such that $ab+1$ divides $a^2+b^2$. Show that $(a^2+b^2)/(ab+1)$ is square of an integer.
    
    \item (2007 IMO) Let $a$ and $b$ be positive integers. Show that if $4ab-1$ divides $(4a^2-1)^2$, then $a=b$.
    
    \item (2005 IMO Shortlisted Problem) Let $a$ and $b$ be positive integers such that $a^n+n$ divides $b^n+n$ for every positive integer $n$. Show that $a=b$.


    

\end{enumerate}

\end{document}