\documentclass[11pt]{scrartcl}
\usepackage[sexy]{evan}
\usepackage[normalem]{ulem}

\renewcommand{\baselinestretch}{1.5}



\begin{document}
	\title{Selected Algebra and Number Theory Problems from JBMO, BMO, and EGMO} % Beginner
	\date{\today}
	\author{Compiled by Azzam}
	\maketitle
	Semua soal tidak terurut berdasarkan kesulitan. Untuk isian alokasi waktu per soal adalah 7,5 menit. Untuk esai, alokasi waktu per soal adalah 30 menit.
	\section{Isian Singkat}
	\begin{soalbaru}(JBMO 2021)
	Let $n$ ($n \ge 1$) be an integer. Consider the equation $2\cdot \lfloor{\frac{1}{2x}}\rfloor - n + 1 = (n + 1)(1 - nx)$, where $x$ is the unknown real variable. Solve the equation for $n = 8$.
	\end{soalbaru}
	
	\begin{soalbaru}(JBMO 2018)
	Find all integers $m$ and $n$ such that the fifth power of $m$ minus the fifth power of $n$ is equal to $16mn$.
	\end{soalbaru}
	
	\begin{soalbaru}(JBMO 2018)
	Find max number $n$ of numbers of three digits such that :
    \begin{enumerate}\item Each has digit sum $9$
\item No one contains digit $0$
\item Each $2$ have different unit digits
\item Each $2$ have different decimal digits
\item Each $2$ have different hundreds digits
    \end{enumerate}
	\end{soalbaru}

    \begin{soalbaru}(JBMO 2020)
    Find all triples $(a,b,c)$ of real numbers such that the following system holds:
$$\begin{cases} a+b+c=\frac{1}{a}+\frac{1}{b}+\frac{1}{c} \\a^2+b^2+c^2=\frac{1}{a^2}+\frac{1}{b^2}+\frac{1}{c^2}\end{cases}$$
    \end{soalbaru}
    
        \begin{soalbaru}(EGMO 2019)
    Find all triples $(a, b, c)$ of real numbers such that $ab + bc + ca = 1$ and $$a^2b + c = b^2c + a = c^2a + b.$$
    \end{soalbaru}
    
    \section{Esai}
    \begin{soalbaru}(BMO 2017)
    Find all ordered pairs of positive integers$ (x, y)$ such that:$$x^3+y^3=x^2+42xy+y^2.$$
    \end{soalbaru}
    
    \begin{soalbaru}(JBMO 2021)
    Let $n$ ($n \ge 1$) be an integer. Consider the equation $2\cdot \lfloor{\frac{1}{2x}}\rfloor - n + 1 = (n + 1)(1 - nx)$, where $x$ is the unknown real variable. Prove that there exists an integer $n$ for which the equation has at least $2021$ solutions. (For any real number $y$ by $\lfloor{y} \rfloor$ we denote the largest integer $m$ such that $m \le y$.)
    \end{soalbaru}
    
    \begin{soalbaru}(BMO 2019)
    Let $\mathbb{P}$ be the set of all prime numbers. Find all functions $f:\mathbb{P}\rightarrow\mathbb{P}$ such that:
$$f(p)^{f(q)}+q^p=f(q)^{f(p)}+p^q$$holds for all $p,q\in\mathbb{P}$.
    \end{soalbaru}

    
    \begin{soalbaru}(JBMO 2004)
    Prove that the inequality\[ \frac{ x+y}{x^2-xy+y^2 } \leq \frac{ 2\sqrt 2 }{\sqrt{ x^2 +y^2 } } \]holds for all real numbers $x$ and $y$, not both equal to 0.
    \end{soalbaru}
    
    \begin{soalbaru}(BMO 2014)
    Let $x,y$ and $z$ be positive real numbers such that $xy+yz+xz=3xyz$. Prove that\[ x^2y+y^2z+z^2x \ge 2(x+y+z)-3 \]and determine when equality holds.
    \end{soalbaru}
\end{document}


