\documentclass{article}
\usepackage{azzam}

\begin{document}

\section*{Algebra}

\begin{enumerate}
    
    \item 
    \begin{enumerate}
        \item A set of 31 real numbers has a sum of 104. A new set is formed by taking each number in the old set and increasing it by 3. What is the sum of the numbers in the new set?
        \item Maddy and Lara see a list of numbers written on a blackboard. Maddy adds 3 to each number in the list and finds that the sum of her new numbers is 45. Lara multiplies each number in the list by 3 and finds that the sum of her new numbers is also 45. How many numbers are written on the blackboard?
    \end{enumerate}

    \item For real numbers $x$ and $y$, define $x \nabla y = x - \dfrac{1}{y}$. Compute $\dfrac{7(2 \nabla (2 \nabla (2 \dots \nabla (2 \nabla 2)\dots)))}{2016 \nabla s}$.

    \item Points $A(0,0)$ and $B(1,1)$ are located on the parabola $y=x^2$. A third point $C$ is positioned on this parabola between $A$ and $B$ such that $AC=CB=r$. What is $r^2$?

    \item Suppose $x>1$ is a real number such that $x + \dfrac{1}{x} = \sqrt{22}$. What is $x^2 - \dfrac{1}{x^2}$?

    \item Find the positive integer $x$ such that $\dfrac{1}{10x} = \dfrac{1}{x^2+x} + \dfrac{1}{x^2+3x+2} + \dfrac{1}{x^2+5x+6}$.

    \item Suppose $a$ and $b$ are real numbers that satisfy the system of equations $a+b=9$ and $a(a-2)+b(b-2)=21$. What is $ab$?

    \item Let $P(x)$ be a quadratic polynomial with real coefficients such that $P(3)=7$ and $P(x) = P(0) + P(1)x + P(2)x^2$ for all real $x$. What is $P(-1)$?

    \item 
    \begin{enumerate}
        \item A line passing through the point $(0,3)$ intersects the graph of $y=x^2$ in two distinct points. The positive difference in $x$-coordinates of these two points is 5. Compute the positive difference between the points' $y$-coordinates.
        \item There exists a positive real number $a$ such that the equation $ax^2 = x+a$ has two real solutions with the property that the larger one is 5 more than the smaller one. What is $a^2$?
    \end{enumerate}

    \item Let $P(x) = x^2+4x+1$. What is the product of all real solutions to the equation $P(P(x))=0$?

    \item A new project begins every two days. Each project will take exactly one more day than the previous one to complete (so the first project takes 3, the second takes 4, and so on). Suppose the new schedule starts on Day 1. On which day will there first be at least 10 projects in place at the same time?

    \item Nonzero real numbers $a, b, c$ satisfy the equations $a^2+b^2+c^2=2915$ and $(a-1)(b-1)(c-1)=abc-1$. Compute $a+b+c$.

    \item Suppose $P(x)$ is a quadratic polynomial with integer coefficients satisfying the identity $P(P(x)) - P(x)^2 = x^2+x+2016$ for all real $x$. What is $P(1)$?

    \item Let $\{a_n\}$ be a sequence of integers such that $a_1=2016$ and $\dfrac{a_{n-1}+a_n}{2} = n^2-n+1$ for all $n \ge 1$. Compute $a_{100}$.

    \item Let $l$ be a real number satisfying the equation $\dfrac{(1+l)^2}{1+l^2} = \dfrac{13}{37}$. Then $\dfrac{(1+l)^3}{1+l^3} = \dfrac{m}{n}$ where $m$ and $n$ are positive relatively prime integers. Find $m+n$.

    \item 2018 little ducklings numbered 1 through 2018 are standing in a line, with each holding a slip of paper with a nonnegative number on it; ducklings 1 and 2018 have the number zero. At some point, ducklings 2 through 2017 simultaneously change their number to equal the average of the numbers of the ducklings to their immediate left and right. Suppose the new numbers sum to 1000. What is the maximum possible sum of the original numbers?

    \item Let $p$ and $q$ be real numbers with $|p|<1$ and $|q|<1$ such that $p+pq+pq^2+pq^3+\dots=2$ and $q+qp+qp^2+qp^3+\dots=3$. What is $100pq$?

    \item Daniel finds a rectangular index card and measures its diagonal to be 8 cm. Daniel then cuts out equal squares of side 1 cm at two opposite corners and measures the distance between the two closest vertices of these squares to be $4\sqrt{2}$ cm. What is the area of the original index card?

    \item The polynomial $x^3-Ax+15$ has three real roots. Two of these roots sum to 5. What is $|A|$?
    
    \item Let $a$ and $b$ be positive real numbers such that $ab=2$ and $\dfrac{a}{a+b^2} + \dfrac{b}{b+a^2} = \dfrac{7}{8}$. Find $a^6+b^6$.

    \item For all real numbers $r$, let $\{r\} = r - \lfloor r \rfloor$. How many real numbers $x \in [1,2)$ satisfy $\{x^{2018}\} = \{x^{2017}\}$?

    \item Quadratic polynomials $P(x)$ and $Q(x)$ have leading coefficients of 2 and $-2$. The graphs of both polynomials pass through (16,54) and (20,53). Find $P(0)+Q(0)$.

    \item Let $\{a_i\}_{i=0}^{\infty}$ be a sequence of real numbers such that $\sum_{n=1}^{\infty}\dfrac{x^n}{1-x^n} = a_0 + a_1x + a_2x^2 + a_3x^3 + \dots$ for all $|x|<1$. Find $a_{1000}$.

    \item Suppose $a, b, c$ and $a, b+1, c+2$ are both geometric sequences. Find the smallest possible value of $(a+b+c)^2$.

    \item Suppose $x, y, z$ are nonzero complex numbers such that $(x+y+z)(x^2+y^2+z^2) = x^3+y^3+z^3$. Compute $(x+y+z)(\dfrac{1}{x}+\dfrac{1}{y}+\dfrac{1}{z})$.

    \item There exists a unique strictly increasing arithmetic sequence $\{a_i\}_{i=1}^{100}$ of positive integers such that $a_1+a_4+a_9+\dots+a_{100}=1000$, where the sum is over $a_{i^2}$ for $1 \le i \le 10$. Find $a_{50}$.

    \item A line with negative slope passing through (18,8) intersects the axes at $(a,0)$ and $(0,b)$. What is the smallest possible value of $a+b$?

    \item Let $a_n = \dfrac{n^2}{2n+1}$, $P = a_1a_2\dots a_{2013}$, and $Q = (a_1+1)(a_2+1)\dots (a_{2013}+1)$. What is the sum of the digits of $\lfloor Q/P \rfloor$?

    \item Nonzero $x,y$ satisfy $3x^2+y^2=13x$ and $x^2+3y^2=14y$. Find $x+y$.

    \item Suppose $n^4 = A\binom{n}{4} + B\binom{n}{3} + C\binom{n}{2} + D\binom{n}{1}$ for all $n \ge 4$. What is $A+B+C+D$?

    \item Nonzero $a,b,c$ satisfy $bc + \dfrac{1}{a} = ca + \dfrac{2}{b} = ab + \dfrac{7}{c} = \dfrac{1}{a+b+c}$. Find $a+b+c$.

    \item Let $p, q, r$ be roots of $x^3-22x^2+80x-67$. If $\dfrac{1}{s^3-22s^2+80s-67} = \dfrac{A}{s-p} + \dfrac{B}{s-q} + \dfrac{C}{s-r}$, what is $\dfrac{1}{A}+\dfrac{1}{B}+\dfrac{1}{C}$?

    \item Let $f$ be a quadratic with leading coefficient 1 tangent to $y=-5x+6$ and $y=x-1$. The sum of the coefficients of $f$ is $\dfrac{p}{q}$. Find $100p+q$.

    \item Nonzero $a,b,c$ satisfy $a+b+c=0$ and $28(a^4+b^4+c^4) = a^7+b^7+c^7$. Find $a^3+b^3+c^3$.

    \item Find the sum of all positive integers $1 \le k \le 99$ such that $x^{100}-ax^k+b = (x^2-2x+1)P(x)$ for some $P$ with integer coefficients.

    \item $u,v$ satisfy $(u-1)(v-1)=9$ and $u^3-u^2=v^3-v^2$. Find the sum of all possible values of $|u|^2+|v|^2$.

    \item Given $\sum_{k=0}^{\infty} \binom{2k}{k} \dfrac{1}{5^k} = \sqrt{5}$, compute $\sum_{k=0}^{\infty} \binom{2k+1}{k} \dfrac{1}{5^k}$.

    \item Real $x,y$ satisfy $x^2+xy+y^2=2$ and $x^2-y^2=\sqrt{5}$. Find the sum of all distinct values of $|x|$ in form $\sum \sqrt{a_i}$. What is $\sum a_i$?

    \item Let $T_n = \dfrac{n(n+1)}{2}$. Compute $\sum_{i=3}^{\infty} \sum_{k=1}^{\infty} (\dfrac{3}{T_i})^k$.

    \item If $a+b=n, a^2+b^2=2n, a^3+b^3=3n$, let $S$ be the sum of all possible values of $a^4+b^4$. Find $S$.

    \item 
    \begin{enumerate}
        \item Roots $r_1,r_2,r_3$ of $x^3-x+1$. Find $\sum \dfrac{1}{r_i^2+r_i+1}$.
        \item Roots $r_1, \dots, r_{20}$ of $x^{20}-7x^3+1$. Find $\sum \dfrac{1}{r_i^2+1}$.
    \end{enumerate}

    \item $f(c)$ is the real $x$ satisfying $\dfrac{x^4+x^5-48}{x^9-1}=c$. Compute $\prod_{c=0}^{47} f(c)$.

    \item $P(x)=x^2-3x-7$. $Q,R$ are monic quadratics. $P+Q, P+R, Q+R$ each pair have a distinct common root. If $Q(0)=2$, find $R(0)$.


    \item Real $x,y$ satisfy $x^2-3y^2=\dfrac{17}{x}$ and $3x^2-y^2=\dfrac{23}{y}$. Find $x^2+y^2$.

    \item Positive $a,b,c,d$ satisfy $(a+b)(c+d)=143, (a+c)(b+d)=150, (a+d)(b+c)=169$. Find the minimum of $a^2+b^2+c^2+d^2$.

    \item $y=x^2$ is rotated acute $\theta$ clockwise about origin to hit axes at 2 points each. If $x$-axis segment is 1, what is the $y$-axis segment length?

    \item Roots $\alpha, \beta, \gamma$ of $x^3-x^2+ax-1$. If $\prod (\alpha^3+1) = 2018$, compute the product of all possible values of $a$.

    \item $f(k)=k^2+k+1$. Find the largest $n$ such that $f(1^2)f(2^2)\dots f(n^2) \ge (f(1)f(2)\dots f(n))^2$.

    \item $P(x)$ is monic quadratic. $P(P(x))=0$ has roots $3,4,a,b$. Find the sum of all values of $(a+b)^2$.
    
    \item $P$ is cubic, $P(0)=3$. $(x^3-2x+1-P(x))(2x^3-5x^2+4-P(x)) \le 0$ for all $x$. Find all values of $P(-1)$.

    \item $(x^2-3x+1)^{1009} = \sum a_k x^k$. Compute the remainder of $\sum a_k^2$ divided by 2017.

    \item $a+\beta+\gamma=6, \alpha^3+\beta^3+\gamma^3=87, (\alpha+1)(\beta+1)(\gamma+1)=33$. Find $\dfrac{1}{\alpha}+\dfrac{1}{\beta}+\dfrac{1}{\gamma}$.

    \item $\sum \dfrac{a}{b+c} = 9, \sum \dfrac{a^2}{b+c} = 32, \sum \dfrac{a^3}{b+c} = 122$. Find $abc$.

    \item Roots $a,b,c$ of $x^3+2x-1=0$. $X,Y$ are possible values of $\dfrac{a}{b}+\dfrac{b}{c}+\dfrac{c}{a}$. Find $(X+1)(Y+1)$.

    \item Non-negative $a_k$ with $\sum a_k=15$ and $\sum ka_k=80$ for $1 \le k \le 10$. Find $M-m$ for $M,m$ max/min of $\sum k^2 a_k$.


    \item $P(x)=x^3-6x-2$ has roots $\alpha, \beta, \gamma$. Find the larger value of $Q(1)$ for quadratics $Q$ passing through $(\alpha,\beta), (\beta,\gamma), (\gamma,\alpha)$.

    \item $P(x) = \prod_{k=1}^{10} (x^{2^k}-x^{2^{k-1}}+1)$. How many terms does $P(x)$ contain?

    \item Find largest $c$ such that non-constant $P$ satisfies $P(z^2)=P(z-c)P(z+c)$. Find $\sum P(1/3)$.

    \item $P$ is tangent to $x$-axis at (5,0) and $y$-axis at (0,12). Find sum of slopes of P-friendly lines.

    \item $abc=1$. $p=(a+b+c)+(1/a+1/b+1/c)$ and $q=a/b+b/c+c/a$. If $p,q \in \mathbb{R}$, find $(p,q)$.

    \item $ab+bc+ac=X$ and $bc+cd+bd=Y$. If $a,b,c,d \ge 0$ and min $a+b+c+d=6\sqrt{3}$, find sum of larger values of obscured integers $X,Y$.

    \item $x^{1000} = \sum \lambda_i F_i(x)$ for Fibonacci polynomials $F_i$. For which $k$ is $|\lambda_k|$ maximized?

\end{enumerate}
\end{document}